The Aquarius Stream Progenitor Was Not a Globular Cluster

### 2012-11-14 2012-aqs/draft-aqs.tex
Start of framework

\title{The First High Resolution Spectroscopic Analysis on the Aquarius Stream}

@@

\section{Observations and Data Analysis}

>>>>

\title{The Aquarius Stream Progenitor Was Not a Globular Cluster}

@@

\section{Observations \& Data Reduction}

\section{Analysis}

\subsection{Radial Velocities}

\subsection{Line Measurements}

\subsection{Stellar Parameters}

\subsection{Model Atmospheres}

\subsection{Abundances}

\begin{deluxetable*}{lccccccc}
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Observed Targets\label{tab:observed-targets}}
\tablehead{
	\colhead{ID} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Air mass} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\mbox{helio}}$} \\
 & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$)
}
\startdata
HD130694  			& 14:50:17.1 & --27:57:41.6 & 1.289 & \nodata & \nodata \\
HD170642  			& 18:32:21.0 & --39:42:12.8 & 1.464 & \nodata & \nodata \\
HD180928  			& 19:18:59.6 & --15:32:11.5 & 1.934 & \nodata & \nodata \\
HD181342  			& 19:21:03.9 & --23:37:09.7 & 1.203 & \nodata & \nodata \\
HD187111 			& 19:48:39.3 & --12:07:17.8 & 1.281 & \nodata & \nodata \\
HD210049  			& 22:08:22.8 & --32:59:14.6 & 1.006 & \nodata & \nodata \\
C2225316-145437  	& 22:25:31.7 & --14:54:39.6 & 1.033 & \nodata & \nodata \\
J221821-183424 		& 22:18:21.2 & --18:34:28.3 & 1.026 & \nodata & \nodata \\
J223504-152834 		& 22:35:04.5 & --15:28:34.9 & 1.047 & \nodata & \nodata \\
J223811-104126 		& 22:38:11.6 & --10:41:29.4 & 1.218 & \nodata & \nodata \\
C2306265-085103		& 23:06:26.6 & --08:51:04.8 & 1.096 & \nodata & \nodata \\
HD219615  			& 23:17:10.7 &$+$03:16:51.9 & 1.412 & \nodata & \nodata 
\enddata
\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
\end{deluxetable*}
